Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-10 CAs_operads.tex
Relecture partie 3 (fin)

    \begin{tikzpicture}[xscale=.18,yscale=.16,Centering]

@@

        \node(r)at(15.00,2.25){};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Higher comb associative operads}
\label{sec:higher_comb_associative_operads}

We run the same algorithm for $\CAs{\gamma}$ when $\gamma \geq 4$.
We obtain the following results.
\medbreak

\Todo{S:remettre la table en forme.}
\begin{center}
  \begin{math} \label{arr:completions_CAs}
    \begin{array}{|c|l|}
      \hline
      \gamma & \mbox{The sequence of first cardinalities of }
       \CAs{\gamma} \mbox{completion}\\ \hline
      1 & 0, 1, 0, 0, \dots \\ \hline
      2 & 0, 0, 1, 0, 0, \dots \\ \hline
      3 & 0, 0, 0, 1, 1, 2, 3, 4, 0, 0, \dots \\ \hline
      4 & 0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22, 11, 12, 15, 19, 25, 36,
       44, 52, 68, 79, 93, 105, 106, 109 \\ \hline
      5 & 0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5, 8, 18, 31, 36, 48, 73, 111,
       172, 272, 455, 783 \\ \hline
      6 & 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 5, 6, 11, 23, 30, 48, 73,
      117, 204, 348, 589, 1004 \\ \hline
      7 & 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 6, 7, 16, 24, 32, 49,
      88, 150, 261, 475, 854\\ \hline
      8 & 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 7, 8, 21, 29,
      34, 53, 93, 172, 311, 565\\ \hline
      9 & 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 8, 9, 28,
      30, 36, 57, 101, 185, 348, 648\\ \hline
    \end{array}
  \end{math}
\end{center}
\medbreak

From these computer explorations, we conjecture that this algorithm
does not provide a finite convergent presentation of $\CAs{\gamma}$,
when $\gamma \geq 4$. We point out that for $\CAs{4}$ new
rewrite rules still appear at degree $41$. Moreover, the total number of
rewrite rules at degree $41$ is $3149$.
\medbreak

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by $\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
\medbreak

We did not find a finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ with one generator when
$\gamma \geq 4$. We discuss the cases with more than one generator in
the perspectives.
\medbreak

\Todo{S: la numérotation de la table n'apparait pas (mais je m'occuperai
de la faire marcher quand je ferai la remise en forme.}
Thanks to the partial completions presented in table
\eqref{arr:completions_CAs}, we can compute the following first
dimensions of $\CAs{\gamma}$.
\begin{center}
  \begin{math} \label{arr:dimensions_CAs}
    \begin{array}{|c|l|}
      \hline
      \gamma & \mbox{The sequence of first dimensions of }
       \CAs{\gamma}\\ \hline
      1 & 1, 1, 2, 5, 14, 42, 132, 429, 1430, 4862, \dots \\ \hline
      2 & 1, 1, 1, \dots \\ \hline
      3 & 1, 1, 2, 4, 8, 14, 20, 19, 16, 14,
          14, 15, 16, 17, \dots \\ \hline
      4 & 1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872,
          105141, 284929, 774254, 2111088,\\
        & 5778420, 15882100, 43837388, 121507230 \\ \hline
      5 & 1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440, 40392, 131997,
          433782, 1432696, 4752857, \\
        & 15829261, 52905635, 177395246 \\ \hline
      6 & 1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431, 52598, 180895,
          626862, 2186504, 7670138, \\
        & 27041833, 95764569 \\ \hline
      7 & 1, 1, 2, 5, 14, 42, 132, 428, 1420, 4796, 16432, 56966, 199444,
          704140, 2503914, 8959699, \\
        & 32236657, 116551168\\ \hline
      8 & 1, 1, 2, 5, 14, 42, 132, 429, 1429, 4851, 16718, 58331, 205632,
          731272, 2620176, 9449688, \\
        & 34276116, 124958386\\ \hline
      9 & 1, 1, 2, 5, 14, 42, 132, 429, 1430, 4861, 16784, 58695, 207452,
          739840, 2658936, 9620232, \\
        & 35011566, 128082515\\ \hline
    \end{array}
  \end{math}
\end{center}
\medbreak

\Todo{S:remettre la table en forme.}

>>>>

    \begin{tikzpicture}[xscale=.18,yscale=.14,Centering]

@@

        \node(r)at(15.00,2.5){};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Higher comb associative operads}
\label{sec:higher_comb_associative_operads}
Let us provide here some experimental data. First,
Table~\ref{tab:dimensions_CAs} shows the first dimensions of the
operads $\CAs{\gamma}$ for $\gamma \in [9]$.
\begin{table}[ht]
    \centering
    \footnotesize
    \setlength{\tabcolsep}{.35em}
    \begin{tabular}{c||ccccccccccccccccc}
        $\gamma$ & \multicolumn{17}{c}{Dimensions of $\CAs{\gamma}$}
        \\ \hline \hline
        1 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4862
        & 16796 & 58786 & 208012 & 742900 & 2674440 & 9694845
        & 35357670
        \\
        2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
        & 1 & 1
        \\
        3 & 1 & 1 & 2 & 4 & 8 & 14 & 20 & 19 & 16 & 14 &
        14 & 15 & 16 & 17 & 18 & 19 & 20
        \\
        4 & 1 & 1 & 2 & 5 & 13 & 35 & 96 & 264 & 724 & 1973 & 5335
        & 14390 & 38872 & 105141 & 284929 & 774254 & 2111088
        %& 5778420 & 15882100 & 43837388 & 121507230
        \\
        5 & 1 & 1 & 2 & 5 & 14 & 41 & 124 & 384 & 1210 & 3861 & 12440
        & 40392 & 131997 & 433782 & 1432696 & 4752857
        & 15829261
        %& 52905635 & 177395246
        \\
        6 & 1 & 1 & 2 & 5 & 14 & 42 & 131 & 420 & 1375 & 4576 & 15431
        & 52598 & 180895 & 626862 & 2186504 & 7670138
        & 27041833
        %& 95764569
        \\
        7 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 428 & 1420 & 4796 & 16432
        & 56966 & 199444 & 704140 & 2503914 & 8959699
        & 32236657
        %& 116551168
        \\
        8 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1429 & 4851 & 16718
        & 58331 & 205632 & 731272 & 2620176 & 9449688 & 34276116
        %& 124958386
        \\
        9 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4861 & 16784
        & 58695 & 207452 & 739840 & 2658936 & 9620232 & 35011566
        %& 128082515
    \end{tabular}
    \medbreak

    \caption{\footnotesize
    The sequences of the cardinalities, arity by arity, of the
    dimensions of~$\CAs{\gamma}$.}
    \label{tab:dimensions_CAs}
\end{table}
\medbreak

Moreover, we run the same completion algorithm for $\CAs{\gamma}$ as
the one considered in Section~\ref{subsubsec:CAs_3}, now for
$\gamma \in [9]$. Table~\ref{tab:cardinalities_completion_CAs} shows
the number of rewrite rules needed to obtain complete orientations.
\begin{table}[ht]
    \centering
    \footnotesize
    \setlength{\tabcolsep}{.35em}
    \begin{tabular}{c||ccccccccccccccccccccccccccc}
        $\gamma$ & \multicolumn{27}{c}{
        Cardinalities of completions of $\CAs{\gamma}$}
        \\ \hline \hline
        1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        2 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        3 & 0 & 0 & 0 & 1 & 1 & 2 & 3 & 4 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        4 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 3 & 4 & 5 & 18 & 22 & 11 & 12
        & 15 & 19 & 25 & 36 & 44 & 52 & 68 & 79 & 93 & 105 & 106 & 109
        \\
        5 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 4 & 5 & 8 & 18 & 31
        & 36 & 48 & 73 & 111 & 172 & 272 & 455 & 783
        \\
        6 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 5 & 6 & 11
        & 23 & 30 & 48 & 73 & 117 & 204 & 348 & 589 & 1004
        \\
        7 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 6 & 7
        & 16 & 24 & 32 & 49 & 88 & 150 & 261 & 475 & 854
        \\
        8 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0
        & 7 & 8 & 21 & 29 & 34 & 53 & 93 & 172 & 311 & 565
        \\
        9 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0
        & 0 & 0 & 8 & 9 & 28 & 30 & 36 & 57 & 101 & 185 & 348 & 648
    \end{tabular}
    \medbreak

    \caption{\footnotesize
    The sequences of the cardinalities, arity by arity, of the rewrite
    rules being completions of orientations of~$\CongrCAs{\gamma}$.}
    \label{tab:cardinalities_completion_CAs}
\end{table}
\Todo{S: erreur dans la table pour $\gamma = 1$ ? Il doit y avoir que
des $0$, j'ai corrigé. Vérifier.}
\Todo{S: il faut équilibrer la table. Toutes les suites doivent avoir
la même longueur. (ou alors, il est toléré d'avoir des suites plus
courtes à mesure que $\gamma$ augmente... mais non ici.)}
From these computer explorations, we conjecture that the algorithm we
use does not provide a finite convergent presentation of $\CAs{\gamma}$,
when $\gamma \geq 4$. We point out that for $\CAs{4}$ new rewrite
rules still appear in arity $42$. Moreover, the total number of rewrite
rules at this arity is~$3149$.
\medbreak

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ when
$\gamma \geq 4$.
\medbreak

\Todo{S: j'ai supprimé les remarques concernant les générateurs multiples
car on n'en a pas du tout parlé pour l'instant. Ça a plus sa place
dans les persp.}
